R Markdown for Reproducible Research

### 2019-01-07 paper.Rmd
add git reference
add some links add author and date

---
title: "R Markdown for Reproducible Research"
output: pdf_document
---

@@

There can be [many reasons](todo) that a user might prefer R Notebooks, but the
most noteworthy difference between R Notebooks and plain R Markdown is that R
Notebooks are somewhat _stateful_. This means that they cache and display output
as it is generated, making it easier to interactively and iteratively build a
narrative without having to re-render the document each time you have made a
change.

@@

There is [much more](todo) available to explore in Parameterized R Markdown,
like an easy-to-use [user interface](todo) for selecting values. You can also
host Parameterized R Markdown in a publishing platform like RStudio Connect that
exposes a user interface to end users of a report.

@@

This process is tedious and error prone: 
 - moving the results to another medium
 - copying values, data, plots, images, etc.
 - injecting values into prose

Moreover, let us imagine that someone wants to reproduce her work, or that
another set of surveys, experiments, or clinical trials are added to her
dataset. Not only must she re-execute her code, she must also duplicate all of
the transmission of information into her manual "publishing" process. If any
data or information is accidentally "left in place" from her first pass, her
results will be un-reproducible and incorrect.

@@

@@

@@

- https://rpubs.com/marschmi/105639
- http://ropensci.github.io/reproducibility-guide/sections/tools/
- http://shop.oreilly.com/product/0636920051435.do
- https://rviews.rstudio.com/2017/03/15/why-i-love-r-notebooks/
- https://rviews.rstudio.com/2018/11/01/r-markdown-a-better-approach/
- https://rviews.rstudio.com/2017/01/25/r-markdown-for-the-enterprise/
- https://rviews.rstudio.com/2018/01/18/package-management-for-reproducible-r-code/
- https://en.wikipedia.org/wiki/Markdown
- https://www.oreilly.com/library/view/the-art-of/9781593273842/ch15.html

>>>>

---
title: "R Markdown for Reproducible Research"
author: "Cole Arendt"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

There can be [many
reasons](https://rviews.rstudio.com/2017/03/15/why-i-love-r-notebooks/) that a
user might prefer R Notebooks, but the most noteworthy difference between R
Notebooks and plain R Markdown is that R Notebooks are somewhat _stateful_. This
means that they cache and display output as it is generated, making it easier to
interactively and iteratively build a narrative without having to re-render the
document each time you have made a change.

@@

There is [much
more](https://bookdown.org/yihui/rmarkdown/parameterized-reports.html) available
to explore in Parameterized R Markdown, like an easy-to-use [user
interface](https://bookdown.org/yihui/rmarkdown/params-knit.html#the-interactive-user-interface)
for selecting values. You can also host Parameterized R Markdown in a publishing
platform like RStudio Connect that [exposes a user interface to end
users](https://docs.rstudio.com/connect/user/param-rmarkdown.html#publish-param-rmarkdown)
of a report.

@@

This process is tedious and error prone: 
 - moving the results to another medium (e.g. from script output to a PowerPoint)
 - copying values, data, plots, images, etc.
 - injecting values into prose (e.g. There are 45 rows in this dataset)

Moreover, let us imagine that someone wants to reproduce her work, or that
another set of surveys, experiments, or clinical trials are added to her
dataset. Not only must she re-execute her code, she must also duplicate all of
the transmission of information into her manual "publishing" process. If any
data or information is accidentally "left in place" from her first pass, her
published results will be un-reproducible and incorrect.

@@

This problem and solution can be reduced to a paradigm of _best practices_ in
which reproducible, data-driven research is greatly simplified by R Markdown.
There are many [much more thorough](https://rpubs.com/marschmi/105639) articles
on the topic, but we will focus on the highlights.

- Define input datasets, resources, or other dependencies
- Manage R packages in a [reproducible
fashion](https://rviews.rstudio.com/2018/01/18/package-management-for-reproducible-r-code/)
- Write narrative and code together into an R Markdown document
- Ensure that the narrative is programmatically dependent on the data
- Configure settings so that the R Markdown document produces final output

## AN EXAMPLE

@@

## INCLUDING PYTHON

## CUSTOMIZED EMAILS

## VERSION CONTROL AND GIT

@@

- https://rpubs.com/marschmi/105639
- http://ropensci.github.io/reproducibility-guide/sections/tools/
- http://shop.oreilly.com/product/0636920051435.do
- https://rviews.rstudio.com/2018/11/01/r-markdown-a-better-approach/
- https://rviews.rstudio.com/2017/01/25/r-markdown-for-the-enterprise/
- https://en.wikipedia.org/wiki/Markdown
- https://www.oreilly.com/library/view/the-art-of/9781593273842/ch15.html
